---
title: "Workout 03"
author: "Akhil Perimbeti"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

library(xml2)
library(rvest)
library(stringr)
library(tm)
library(wordcloud)
library(ggplot2)
library(dplyr)
```

## 1) Extract Simple Information of the Authors
<br/>
```{r}
# Paul Romer data

download.file('https://raw.githubusercontent.com/ucb-stat133/stat133-fall-2019/master/data/scholar/paul_romer_GoogleScholarCitations.html',destfile = "paul_romer_GoogleScholarCitations.webarchive")

rawdat1 =read_html('https://raw.githubusercontent.com/ucb-stat133/stat133-fall-2019/master/data/scholar/paul_romer_GoogleScholarCitations.html')

table1 <- html_table(rawdat1)

save(rawdat1, file = "/Users/akhilperimbeti/Desktop/workout03/data/rawdata/scholarA_GoogleScholarCitations.html")
# William Nordhaus data

download.file('https://raw.githubusercontent.com/ucb-stat133/stat133-fall-2019/master/data/scholar/william_nordhaus_GoogleScholarCitations.html',destfile = "william_nordhaus_GoogleScholarCitations.webarchive")

rawdat2 =read_html('https://raw.githubusercontent.com/ucb-stat133/stat133-fall-2019/master/data/scholar/william_nordhaus_GoogleScholarCitations.html')

table2 <- html_table(rawdat2)

save(rawdat2, file = "/Users/akhilperimbeti/Desktop/workout03/data/rawdata/scholarB_GoogleScholarCitations.html")
```

<br/> 

(a) Extracting Scholar Names
```{r}

# Scholar A (Paul Romer)

name1 <- rawdat1 %>% html_nodes(xpath = '//*[@id="gsc_prf_in"]') %>% html_text
name1

# Scholar B (William Nordhaus)

name2 <- rawdat2 %>% html_nodes(xpath = '//*[@id="gsc_prf_in"]') %>% html_text
name2

```

<br/> 

(b) Extracting Institutions affiliated with each scholar

```{r}
# Institution Affiliated with Scholar A

institution1 <- rawdat1 %>% html_nodes(xpath = '//*[@class="gsc_prf_il"]') %>% html_text
if (length(strsplit(institution1, ",")) == 0) {
  sa_institution = NA
} else {
  sa_institution = strsplit(institution1, ",")[[1]][2]
}
sa_institution

# Institution Affiliated with Scholar B

institution2 <- rawdat2 %>% html_nodes(xpath = '//*[@class="gsc_prf_il"]') %>% html_text
if (length(strsplit(institution2, ",")) == 0) {
  sb_institution = NA
} else {
  sb_institution = strsplit(institution2, ",")[[1]][2]
}
sb_institution

```

<br/>

## 2) Extract All The Papers For Each Author (Not Just The 20 Most Cited)
<br/>
```{r}

#CLEAN DATA

table_citations1=table1[[1]]
long_info1=table1[[2]][1]
citation1=table1[[2]][2]
year1=table1[[2]][3]


table_citations2=table2[[1]]
long_info2=table2[[2]][1]
citation2=table2[[2]][2]
year2=table2[[2]][3]

info_link1=rawdat1%>% html_nodes(xpath='//*[@id="gsc_a_b"]')%>%html_nodes(xpath='tr')%>%html_nodes(xpath='td')
result1=sapply(html_children(info_link1),html_text)
result1=result1[result1!='*']

info_link2=rawdat2%>% html_nodes(xpath='//*[@id="gsc_a_b"]')%>%html_nodes(xpath='tr')%>%html_nodes(xpath='td')
result2=sapply(html_children(info_link2),html_text)
result2=result2[result2!='*']


df1_citations=data.frame(article_title=result1[seq(1,length(result1),5)],
                         
author=result1[seq(2,length(result1),5)],
                       journal=result1[seq(3,length(result1),5)],
                       citations=result1[seq(4,length(result1),5)],
                       year=result1[seq(5,length(result1),5)])


df2_citations =data.frame(article_title=result2[seq(1,length(result2),5)],
                       author=result2[seq(2,length(result2),5)],
                       journal=result2[seq(3,length(result2),5)],
                       citations=result2[seq(4,length(result2),5)],
                       year=result2[seq(5,length(result2),5)])

save(df1_citations, file= "/Users/akhilperimbeti/Desktop/workout03/data/cleandata/scholarA_GoogleScholarCitations.csv")
save(df2_citations, file= "/Users/akhilperimbeti/Desktop/workout03/data/cleandata/scholarB_GoogleScholarCitations.csv" )

final_df=rbind(df1_citations,df2_citations)

head(final_df, 5)
tail(final_df, 5)

```


## 3) Practice with Regular Expressions
<br/>
(a) Paper titles that begin with a vowel

```{r}
# Paul Romer vowels
paul_vowels=0
for (i in 1:length(df1_citations[[1]])){
 if (substr(df1_citations[[1]][i],1,1)== "A" |substr(df1_citations[[1]][i],1,1)=="I" | substr(df1_citations[[1]][i],1,1)=="E"|substr(df1_citations[[1]][i],1,1)=="O"|substr(df1_citations[[1]][i],1,1)=="U"){paul_vowels = paul_vowels+1}
}

paul_vowels

# William Nordhaus vowels

william_vowels <- 0
for (i in 1:226) {
  if(any(substring(df2_citations[[1]][i], 1, 1) == c("A", "E", "I", "O", "U")) == TRUE) {
    william_vowels <- william_vowels + 1
  } 
}
william_vowels

```

<br/>

(b) Paper titles ending with "s"

```{r}

# "S" beginning papers for Paul Romer

paulpaper=0

for (i in 1:length(df1_citations[[1]])){
  a=nchar(substr(df1_citations[[1]][i],1,10000))
  if (substr(df1_citations[[1]][i],a,a)== "s"){paulpaper=paulpaper+1}
}
paulpaper

# "S" beginning paper for William Nordhaus

williampaper=0

for (i in 1:length(df2_citations[[1]])){
  a=nchar(substr(df2_citations[[1]][i],1,10000))
  if (substr(df2_citations[[1]][i],a,a)== "s"){williampaper=williampaper+1}
}
williampaper

```

<br/>

(c) Longest Paper Titles for each author

```{r}

# Longest Title for Paul Romer
paultitle=0

for (i in 1:length(df1_citations[[1]])){
  x=nchar(substr(df1_citations[[1]][i],1,10000))
  if (x >paultitle){
    paultitle=x 
    y=i}
}
paultitle

substr(df1_citations[[1]][y],1,100000000)

# Longest Title for William Nordhaus
willtitle=0

for (i in 1:length(df2_citations[[1]])){
  x=nchar(substr(df2_citations[[1]][i],1,10000))
  if (x > willtitle){
    willtitle= x 
    y=i}
}

willtitle

substr(df2_citations[[1]][y],1,100000000)

```

<br/>

(d) Variable number of punctuation symbols in titles. Summary stats and histograms

```{r}

# Paul Romer's symbols and histogram
paul_punctuation <- (str_count(df1_citations[[1]], "[:punct:]"))
summary(paul_punctuation)
hist(paul_punctuation, main = "Total # of punctuation symbols in Romer Titles", xlab = "# of punctuation per title")

# William Nordhaus' symbols and histogram
william_punctuation <- (str_count(df2_citations[[1]], "[:punct:]"))
summary(william_punctuation)
hist(william_punctuation, main = "Total # of punctuation symbols in Nordhaus Titles", xlab = "# of punctuation per title")
```

<br/>

(e) Removing words --> the, a, an, and, in, if, but as well as numbers and punctuation from the titles.


```{r}
stop_words <- c("the", "a", "an", "and", "in", "if", "but", "of", "to", "from", "for", "on")

# Paul Romer titles without stop words, punctuation and numbers
low_df1 <- tolower(df1_citations[[1]])
p1 <- c()
s1<- c()

for (i in 1:226) {
  p1[i] <- removePunctuation(low_df1[i])
  p1[i] <- removeWords(p1[i], stop_words)
  p1[i] <- removeNumbers(p1[i])
  s1 <- c(s1, strsplit(p1[i], "\\s+")[[1]])
}
head(s1,20)

# William Nordhaus titles without stop words, punctuation and numbers
low_df2 <- tolower(df2_citations[[1]])
p2 <- c()
s2<- c()

for (i in 1:226) {
  p2[i] <- removePunctuation(low_df2[i])
  p2[i] <- removeWords(p2[i], stop_words)
  p2[i] <- removeNumbers(p2[i])
  s2 <- c(s2, strsplit(p2[i], "\\s+")[[1]])
}
head(s2,20)
```

<br/>

(f) Scholar A (Paul Romer) 10 most frequent words


```{r}

# Paul Rober's Top Ten Most Frequent Words
x=str_replace_all(df1_citations$article_title,"\\sthe\\s"," ")
words=table(tolower(unlist(strsplit(x,split=" "))))

words["and"]=0
words["the"]=0
words["of"]=0
words["in"]=0
words["from"]=0
words["an"]=0
words["a"]=0
words["to"]=0
words["for"]=0
words["on"]=0
head(sort(words,decreasing=TRUE),10)
```
<br/>

(g) Scholar B (William Nordhaus) 10 most frequent words

```{r}
# William Norhaus' Top Ten Most Frequent Words
y=str_replace_all(df2_citations$article_title,"\\sthe\\s"," ")
words=table(tolower(unlist(strsplit(y,split=" "))))

words["and"]=0
words["the"]=0
words["of"]=0
words["in"]=0
words["from"]=0
words["an"]=0
words["a"]=0
words["to"]=0
words["for"]=0
words["on"]=0
head(sort(words,decreasing=TRUE),10)

```
<br/>

## 4) Data Visualization

<br/>


1. WordClouds for the titles of both authors
- For Paul Romer, the most commomn occuring words are 'Economic' and "growth"
- For William Nordhaus, the most commomn occuring words are 'Economic', "global", "climate"
<br/>

```{r}

#Word Cloud for Paul Romer's Work
docs1 <- Corpus(VectorSource(s1))
dtm1 <- TermDocumentMatrix(docs1) 
mat1 <- as.matrix(dtm1) 
words1 <- sort(rowSums(mat1),decreasing=TRUE) 
df1 <- data.frame(word = names(words1),freq=words1)
set.seed(12345)

png("/Users/akhilperimbeti/Desktop/workout03/images/wordcloud1.png",
  width = 3.25,
  height = 3.25,
  units = "in",
  res = 1200,
  pointsize = 4)
par(
  mar      = c(5, 5, 2, 2),
  xaxs     = "i",
  yaxs     = "i",
  cex.axis = 2,
  cex.lab  = 2)
wordcloud1 <- wordcloud(words = df1$word, freq = df1$freq, min.freq = 1, max.words=Inf, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Paired"), scale=c(3.5,0.25))
dev.off()

#Word Cloud for William Nordhaus Work
docs2 <- Corpus(VectorSource(s2))
dtm2 <- TermDocumentMatrix(docs2) 
mat2 <- as.matrix(dtm2) 
words2 <- sort(rowSums(mat2),decreasing=TRUE) 
df2 <- data.frame(word = names(words2),freq=words2)
set.seed(12345)

png("/Users/akhilperimbeti/Desktop/workout03/images/wordcloud2.png",
  width = 3.25,
  height = 3.25,
  units = "in",
  res = 1200,
  pointsize = 4)
par(
  mar      = c(5, 5, 2, 2),
  xaxs     = "i",
  yaxs     = "i",
  cex.axis = 2,
  cex.lab  = 2)
wordcloud2 <- wordcloud(words = df2$word, freq = df2$freq, min.freq = 1, max.words=Inf, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Paired"), scale=c(3.5,0.25))
dev.off()
```

<br/>

2. Line Plot displaying the number of the publications for the two scholars across years.
<br/>

```{r}

years <- 1974:2019

dat1 <- tail(table1[[2]][3][[1]][which(table1[[2]][3][[1]] != "")], -1)
count1 <- c(ftable(dat1)[1:2], rep(0, 11), ftable(dat1)[3], 0, ftable(dat1)[4:34])

dat2 <- tail(table2[[2]][3][[1]][which(table2[[2]][3][[1]] != "")], -1)
count2 <- c(rep(0, 14), ftable(dat2)[1], rep(0, 2), ftable(dat2)[2], rep(0, 3), ftable(dat2)[3], 0, ftable(dat2)[4], 0, ftable(dat2)[5:25])

df_plot<- data.frame(years, count1, count1)

png("/Users/akhilperimbeti/Desktop/workout03/images/number_of_publications.png",
  width = 3.25,
  height = 3.25,
  units = "in",
  res = 1200,
  pointsize = 4)
par(
  mar      = c(5, 5, 2, 2),
  xaxs     = "i",
  yaxs     = "i",
  cex.axis = 2,
  cex.lab  = 2)
ggplot(df_plot, aes(x=years)) + geom_line(aes(y=count1), color = "blue") + geom_line(aes(y=count2), color = "red") + ylab("Number of Publications") + xlab("Years") + theme(legend.position="right")
dev.off()
```

##5) Answers to Questions
<br/>
```{r}

table_citations1=table1[[1]]
long_info1=table1[[2]][1]
citation1=table1[[2]][2]
year1=table1[[2]][3]

table_citations1

table_citations2=table2[[1]]
long_info2=table2[[2]][1]
citation2=table2[[2]][2]
year2=table2[[2]][3]

table_citations2

```

Q1: On Average, The author William Norhaus has more co-authors
<br/>
Q3 : No, the two scholars have never collaborated on a paper together
<br/>
Q4 : The Paper with the most co-authors is "Economic growth and business cycles: The labor supply decision with two types of technological progress"
<br/>
Q6: There does not seem to be a set correlation between number of pages in an article and the number of citations.
<br/>
Q8: According to the tables above, the total number of citations for Paul Romer is 85,359 and the total number of citations for William Nordhaus is      65,484. So TOTAL number of citations is 150,843
<br/>
Q9: According to the citations data, I believe the author Paul Romer is the most influential in his field. He mainly delves into economic growth and     has a very significant number of citations(85,359)